Will it blend: Is the Milky Way bar causing chaotic fanning of the Ophiuchus stream?

### 2015-09-04 ms.tex
text

To integrate orbits and to compute chaos indicators we must choose a gravitational potential model to represent the potential of the Milky Way. The key feature of the potential that we would like to capture is the time-dependence and triaxiality of the Galactic bar. We construct two parametrized potential models: one with a triaxial, time-dependent bar and one with a purely spherical bulge, both added to simple models for the disk and halo of the Milky Way. Recent work has mapped the 3D density distribution of the region around the bulge using number counts of red clump stars and have measured the bar angle and axis ratios of the bar structure \citep{wegg13}. The authors do not fit an analytic density model to the data and do not provide enough information about the density field to reconstruct the full-space stellar density distribution of the bar. Further, this is not a dynamical model for the bar and therefore may not account for all of the mass but rather provides information about the number density of stars in the Galactic bar.

>>>>

To integrate orbits and to compute chaos indicators we must choose a gravitational potential model to represent the potential of the Milky Way. The key feature of the potential that we would like to capture is the time-dependence and triaxiality of the Galactic bar. We construct two parametrized potential models: one with a triaxial, time-dependent bar and one with a purely spherical bulge, both added to simple models for the disk and halo of the Milky Way. Recent work has mapped the 3D density distribution of the region around the bulge using number counts of red clump stars and have measured the bar angle and axis ratios of the bar structure \citep{wegg13}. The authors do not fit an analytic density model to the data and do not provide enough information about the density field to reconstruct the full-space stellar density distribution of the bulge. Further, this is not a dynamical model for the bar and therefore may not account for all of the mass but rather provides information about the number density of stars in the Galactic bar. \cite{portail15}
